The importance of measurement uncertainty in ecological management

### 2018-01-04 manuscripts/manuscript.Rmd
tweaking extrafont issues

```{r suggested_libs}
library(hrbrthemes)
library(extrafont)
##extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
extrafont::loadfonts()
hrbrthemes::import_roboto_condensed()     # One-time use to set up fonts 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

>>>>

```{r suggested_libs}
library(hrbrthemes)
#library(extrafont)
##extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
#extrafont::loadfonts()
hrbrthemes::import_roboto_condensed()     # One-time use to set up fonts 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```
